Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-09-02 final.tex
up

 A {\em well-quasi-ordering} (wqo) is any quasi-ordering $(X,\leq)$ such that, for any infinite sequence $x_0, x_1, x_2, ...$ in $X$, there exist indexes $i \leq j$ with $x_i \leq  x_j$.
%
%
%
Wqo admits many other equivalent formulations. 
%
%
As an example, $(\N^d, \leq)$, the set of vectors of $d$ natural numbers (where $d$ is finite) with component-wise order is a wqo.
%
Quasi-orderings that have no 
infinite subset of mutually incomparable elements (antichains)
 enjoy a similar \emph{finite decomposition} property than wqo: every downward-closed subset $D \subseteq X$ can be decomposed into a \emph{finite} set of ideals $J_1, J_2,..., J_n$ such that $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$.
%
%
In what follows, a downward-closed set $D$ is represented by its finite set of ideals (or by the minimal elements of its upward-closed complement), and an upward-closed set $U$ is represented by its finite set of minimal elements. \\

>>>>

 A {\em well-quasi-ordering} (wqo) is any quasi-ordering $(X,\leq)$ such that, for any infinite sequence $x_0, x_1, x_2, ...$ in $X$, there exist indexes $i \leq j$ with $x_i \leq  x_j$.
%
%
%
Wqo admits many other equivalent formulations. 
%
%
As an example, $(\N^d, \leq)$, the set of vectors of $d$ natural numbers (where $d$ is finite) with component-wise order is a wqo.
%
Quasi-orderings that have no 
infinite subset of mutually incomparable elements (antichains)
 enjoy a similar \emph{finite decomposition} property than wqo: every downward-closed subset $D \subseteq X$ can be decomposed into a \emph{finite} set of ideals $J_1, J_2, \ldots, J_n$ such that $D = \downarrow (J_1 \cup J_2 \cup \ldots \cup J_n)$.
%
%
In what follows, a downward-closed set $D$ is represented by its finite set of ideals (or by the minimal elements of its upward-closed complement), and an upward-closed set $U$ is represented by its finite set of minimal elements. \\
